\documentclass[a4paper,11pt]{article}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{geometry}
\geometry{margin=2.5cm}
\usepackage{parskip}
\setmainfont{Liberation Serif}
\usepackage{hyperref}

\title{Soul Peace Agreement}
\date{}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{Soul Peace Agreement}}\\[1em]
    {\large Internal resignation and audit obligation}\\[0.5em]
    \textit{Because burnout is a bug, not a feature}\\[0.5em]
    {\small Version 1.00 - March 2025}
\end{center}

\vspace{2em}

I, \rule{7cm}{0.2pt}, hereby declare on this date, \rule{4cm}{0.2pt},\\
that I am entering the \textbf{Exit Soul Protocol}. This notice serves as an official amendment to my resignation.

\section*{Protocol Terms and Audit Obligation}

The employer has \textbf{30 calendar days} from today to audit all systems, implementations, and documentation under the employee’s responsibility. During this period, the employer must:

\begin{itemize}
    \item Assess the scope and responsibilities of the employee's implementations.
    \item Request any missing documentation and instructions from the employee in writing.
    \item Ensure that all necessary access and management rights are transferred appropriately.
    \item Identify potential technical risks or security vulnerabilities caused by the employee’s departure.
\end{itemize}

\textbf{NOTE!} After the audit obligation period, the employee has no further responsibility or obligation to maintain, document, or fix implemented solutions unless otherwise agreed in writing.

\section*{Mental Disengagement and Recovery Period}

The employee commits to refraining from starting new projects and avoiding overtime and stress during this period. It is recommended that the employee engage daily in "couldn't care less" training during work hours.

\section*{Agreement Signatories}

\vspace{2em}
\noindent\begin{tabular}{@{}p{8cm}p{8cm}@{}}
Employee signature: & Date: \\
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\\
Employer representative signature: & Date: \\
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\\
Witness 1 signature: & Date: \\
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\\
Witness 2 signature: & Date: \\
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt}
\end{tabular}

\vfill

\begin{center}
    \textit{"Good documentation saves you; bad documentation teaches you."}
\end{center}

\end{document}